--- 
title: "Oryx-MRSI Documentation"
author: "Sevim Cengiz, Muhammed Yildirim, Abdullah Bas, Esin Ozturk Isik"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: ""
---

## Features

- ```Main Page``` The user needs to provide parameters for the 3D multivoxel 1H-MRSI data.
  Required parameters: 
 
   a. exclusion criteria for fCSF, SNR, FWHM, CRLB 
 
   b. RF bandwidhth of the system for chemical shift correction 
 
   c. cut-off value for the probabilistic binary map after registration

- ```Load Data``` Reads the raw 1H-MRSI data and LCModel otput files for raw data and Coord file visualization of spectra.

- ```Co-registration``` Coregisters FOV,Press-Box(VOI), all voxels of spectra considering chemical shift correction if chemical shift correction is 'On'.

- ```Segmentation``` Calculation of WM, GM, CSF fractions in each voxel of all metabolites considering chemical shift correction. 

- ```FWHM-SNR``` Visualization of FWHM and SNR values for all voxels

- ```Included Voxels``` Visualization of included voxels into the 1H-MRSI data analysis after exclusion criteria values considering FWHM, SNR, CRLB, and fCSF. 

- ```Metabolite Map``` All metabolite results are used to create metabolite maps including: 
  - concentration map,
  - concentation map to Ins or Cr+PCr ratio 
  - CSF corrected concentration map, 
  - CSF corrected concentration map to Ins or Cr+PCr ratio.

- ```Registration``` Generates MNI-Registered metabolite maps including the outputs created in the previous module.

- ```ROI Analysis``` Region of interest (ROI) analysis at multiple brain atlases like [Schafer2018 100/400 Parcels on 7 resting-state (rs-fMRI) networks](https://pubmed.ncbi.nlm.nih.gov/28981612/) or [MNI thr 0/25/50 brain regions](https://fsl.fmrib.ox.ac.uk/fsl/fslwiki/Atlases). 


Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

## Oryx-MRSI 

```{r logo, fig.cap=' ', out.width='80%', fig.asp=.75, fig.align='left'}
```
Oryx-MRSI is a fully automated software for a comprehensive analysis of multi-slice proton magnetic resonance spectroscopic imaging (1H-MRSI) data. 



## Release 

Version 1.0

## Licencing 

Apache-2.0 License

## Developers

- Sevim Cengiz

- Muhammed Yildirim

- Abdullah Bas

- Esin Ozturk Isik

Should you publish material that made use of Oryx-MRSI, please cite the following publication:

Cengiz S, Yildirim M, Bas A, Ozturk-Isik E. ORYX-MRSI: A data analysis software for multi-slice 1H-MRSI. International Society for Magnetic Resonance in Medicine. Virtual Meeting, May 15-20, 2021.  (Digital Poster)


## Acknowledgements

- This project was funded by TUBITAK 115S219. We thank all open-source MR and MRS tools.

- Oryx-MRSI uses some functions of [FID-A](https://github.com/CIC-methods/FID-A), check [this link](https://github.com/CIC-methods/FID-A/blob/master/LICENSE.txt) for licence.

- Oryx-MRSI uses some functions of [Gannet](https://github.com/richardedden/Gannet3.1).

    - Edden RAE, Puts NAJ, Harris AD, Barker PB, Evans CJ. Gannet: A batch-processing tool for the quantitative analysis of gamma-aminobutyric acid-edited MR      spectroscopy spectra. J. Magn. Reson. Imaging 2014;40:1445–1452. doi: 10.1002/jmri.24478)

- Oryx-MRSI uses some functions of [Osprey](https://github.com/schorschinho/osprey), check [this link](https://github.com/schorschinho/osprey/blob/develop/LICENSE.md) for licence.

    - G Oeltzschner, HJ Zöllner, SCN Hui, M Mikkelsen, MG Saleh, S Tapper, RAE Edden. Osprey: Open-Source Processing, Reconstruction & Estimation of Magnetic Resonance Spectroscopy Data. J Neurosci Meth 343:108827 (2020).

- Oryx-MRSI uses some functions of [MRS_MRI_libs](https://github.com/chenkonturek/MRS_MRI_libs), check [this link](https://github.com/chenkonturek/MRS_MRI_libs/blob/master/LICENSE) for license.

- Oryx-MRSI uses some functionf of [NIFTI-Matlab](https://github.com/NIFTI-Imaging/nifti_matlab), check [this link](https://github.com/NIFTI-Imaging/nifti_matlab/blob/master/license.txt) for licence.

- Oryx-MRSI uses some functions written by [Jamie Near](https://www.mcgill.ca/psychiatry/jamie-near) (McGill University)

- Oryx-MRSI uses some functions written by [H.Ratiney](https://www.creatis.insa-lyon.fr/site7/en/users/ratiney) (CREATIS-LRMN) 

- Oryx-MRSI uses Schaefer2018_100/400Parcels_7Networks_order_FSLMNI152_2mm.nii. See Github [link](https://github.com/ThomasYeoLab/Standalone_CBIG_fMRI_Preproc2016), for [licence](https://github.com/ThomasYeoLab/Standalone_CBIG_fMRI_Preproc2016/blob/master/LICENSE.md).

- Oryx-MRSI uses MNI152_T1_2mm_brain.nii.gz, MNI-maxprob-thr0/25/50-2mm.nii.gz acquired from [FSL](https://fsl.fmrib.ox.ac.uk/fsl/fslwiki/Atlases), for [licence](https://fsl.fmrib.ox.ac.uk/fsl/fslwiki/Licence). 

- If there is any function that I forget to mention about name/link/citation, please let me know.



This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Getting Started

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

