--- 
title: "Oryx-MRSI Documentation"
author: "Sevim Cengiz, Muhammed Yildirim, Abdullah Bas, Esin Ozturk Isik"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "Oryx-MRSI Documentation"
---

# Prerequisites

- [MATLAB R2020b](https://www.fil.ion.ucl.ac.uk/spm/software/download/)

- [FSL](https://fsl.fmrib.ox.ac.uk/fsl/fslwiki/FSL) for FLIRT 

- [SPM12](https://www.fil.ion.ucl.ac.uk/spm/software/download/)

- [GUI Layout Toolbox](https://www.mathworks.com/matlabcentral/fileexchange/47982-gui-layout-toolbox)

- [Widgets Toolbox](https://www.mathworks.com/matlabcentral/fileexchange/66235-widgets-toolbox-compatibility-support)

- **Oryx-MRSI** is tested on MAC (2.9 GHz Quad-Core Intel Core i7, 16 GB 2133 MHz LPDDR3, Radeon Pro 560 4 GB
Intel HD Graphics 630 1536 MB ) and Ubuntu 18.04.4 LTS (Memory 32GIB, Processor Intel Core i7-9800X CPU @3.8GHzx16, Graphics GeForce RTX 2070/PCle/SSE2)


This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
